intro

### 2022-02-17 06_Paper/ER-ED/TheoreticalBackground.Rmd
Update TheoreticalBackground.Rmd

We assume that people choose the strategy that has the highest value for them at that moment.
The value is determined against the background of goal achievement in the specific situation: A strategy is highly valued if it facilitates goal achievement [@Aldao2015]. 
One certainly central goal is the regulation of negative affect.
A second, intrinsic and rather less obvious goal is the avoidance of effort [@Inzlicht2018].
When given the choice, most individuals prefer tasks that are less effortful [@Hull1943].
We assume that both aspects are set off against each other by individuals to determine individual subjective values (SVs) of ER strategies: A strategy is more valuable if it can reduce emotional arousal *and* is less effortful.
SVs of ER Strategies could be helpful to describe the ER repertoire [@Aldao2015] more comprehensively.
Depending on the flexibility of a person, different patterns of SVs could be conceivable: A person with high flexibility would show relatively high SVs for a number of strategies.
This would mean that all strategies are a good option for goal achievement.
A second person with less flexibilty, however, would show high SVs only for one strategy, or for no strategy at all.
This in turn would mean that no strategy is a good choice to achieve goals.

>>>>

We assume that people choose the strategy that has the highest value for them at that moment.
The value is determined against the background of goal achievement in the specific situation: A strategy is highly valued if it facilitates goal achievement [@Aldao2015]. 
One certainly central goal is the regulation of negative affect.
A second, intrinsic and rather less obvious goal is the avoidance of effort [@Inzlicht2018].
When given the choice, most individuals prefer tasks that are less effortful [@Hull1943].
We assume that both aspects are traded off against each other by individuals to determine individual subjective values (SVs) of ER strategies: A strategy is more valuable if it can reduce emotional arousal *and* is less effortful.
SVs of ER Strategies could be helpful to describe the ER repertoire [@Aldao2015] more comprehensively.
Depending on the flexibility of a person, different patterns of SVs could be conceivable: A person with high flexibility would show relatively high SVs for a number of strategies.
This would mean that all strategies are a good option for goal achievement.
A second person with less flexibilty, however, would show high SVs only for one strategy, or for no strategy at all.
This in turn would mean that no strategy is a good choice to achieve goals.
